%  Targets
\infolevone{
\chapter[Target System]{Target System}
\footnote{Authors: S. Stepanyan \email{stepanya@jlab.org}}
}
\infoleveqnull{\section{Target Systems}}

The HPS target system consists of several solid material foils mounted on a target ladder. The bottom edge of the foils mounted on the ladder is free-standing so there
is no thick support frame to trip the beam when the target is inserted. Target position is adjustable vertically allowing different targets to be inserted. The support
frame on the beam-right side of the target is made thin enough to
prevent excessive flux of secondaries and radiation damage to the silicon detector in the event of an errant
beam caused, for example, by an chicane magnet trip which will move beam to the right.
               
\subsection{Hazards} 

\indent

There are hazards related to moving the target frame into the beam or overheating the target foils. The stepping motor linear
actuator will be operated using EPICS controls, GUI for operation of the target will have preset coordinates for each target foil.  
The tungsten targets are intended to operate with beam currents up to $500$ nA, which produce strong local heating. The strength of tungsten drops by an order of magnitude with temperature increases in the range of 1000 C. In addition, the material re-crystallizes above
this range, which increases the tendency for cracking where thermal expansion has caused temporary dimpling. 

\subsection{Mitigations}

\indent

There will be limit switches (hard stops) that will prevent motion of the target ladder outside of allowed range if EPICS set values are wrong. To keep the temperature rise less than
about 1000 degrees is accomplished by selecting an
adequately large beam spot area. There will be overall beam current limit of $500$ nA for the experiment.

\subsection{Responsible Personal}

\indent

The target system will be maintained by the Hall B engineering group.  

 \begin{table}[!htb]
 \centering
 \begin{tabular}{|c|c|c|c|c|}
\hline
 Name&Dept.&Phone&email&Comments \\ \hline
 Tech-on-call & Hall-B&&& 1st contact  \\ \hline
 D. Tilles & Hall-B&&tilles@jlab.org&2nd contact \\ \hline
C. Field& SLAC&&sargon@slac.stanford.edu&contact \\ \hline
 \end{tabular}
\caption{ Personal responsible for the target.} 
\label{tb:beam}
\end{table}

