%
% details for each of the Halls
%
\chapter{Hall Specific Equipment}

\section{Overview}


The following Hall B subsystems are considered part of the experimental endstation equipment for running the Heavy Photon Search (HPS) experiment engineering run.
Many of these subsystems impose similar hazards, such as those induced by magnets and magnet power supplies,
high voltage systems and vacuum systems.  Note that a specific sub-system may have many uniquet hazards associated with it.
For each major system, the hazards, mitigations, and responsible personnel are noted.

The material in this chapter is a subset of the material in the full Hall B operations manual and is only intended to familiarize
people with the hazards and responsible personnel for these systems.  It in no way should be taken as sufficient information to use or operate this equipment.

\section{Checking Tie-in To Machine Fast Shutdown System}

In order to make sure that hall equipment that should be tied into the machine fast shutdown (FSD) system
has been properly checked, the hall work coordinator must be notified by e-mail prior to the end of each
installation period by the system owner
that the checks have been performed in conjunction with accelerator operations (i.e. checking that equipment's signals
will in fact cause an FSD).  These notifications will be
noted in the work coordinator's final check-list as having been done.   System owners are responsible
for notifying the work coordinator that their system has an FSD tie-in so it can be added to the check-list.


%
% include your Hall sections here
%
