\graphicspath{{hps/figs/}}
\renewcommand{\dirfig}[0]{hps/figs}
\renewcommand{\dircur}[0]{hps}
\input{hps/intro}
\input{hps/beam}
\infolevone{
\part{HPS Spectrometer}
}
\input{hps/hpsmag}
\input{hps/tgtcham}
\input{hps/vacuum}
\input{hps/trk}
\input{hps/pid}


\section{CLAS12 Construction work}
\indent

The main 12 GeV activity in Hall-B during the HPS engineering run will be assembly of the CLAS12 Torus magnet. Beam running would occur during evenings, nights, and weekends or during other periods when it would not conflict with the regularly scheduled assembly of the CLAS12 Torus coils.

\subsection{Hazards} 
\indent

There are no personal hazards associated with the running over evenings, nights, and weekends, and continue with torus assembly during the normal work hours. The only hazard is possible delays of start of the torus work after beam the delivery due to possible activation of beamline parts close to the torus assembly fixtures.
 
\subsection{Mitigations}
\indent

Every time Hall will switch from beam running to torus assembly, a fully survey of the hall will be conducted and Hall will be brought to "Restricted Access". Normally this will happen very early in the morning of work day (6am). If elevated radiation near torus assembly fixtures are found, work on torus must be delayed until conditions are acceptable. 

However, we do not expect any excess radiation in the Hall or activation of any beam line components near the torus assembly area. The HPS  target is located $\sim20$ meters upstream of the assembly area and only tuned electron beam, couple of hundred micron wide, will be transported in vacuum through hall to the target. If beam conditions are not acceptable, which may result excess radiation, beam tune will be performed. Every time beam tune is required the Hall-B tagger magnet will be energized and beam will be dumped on the Hall-B tagger dump, shielded hole in the floor $\sim 15$ meters upstream of the torus assembly area. 

\subsection{Responsible Personnel}
\indent

Individuals responsible for the coordination of the torus assembly and HPS engineering run:

\begin{table}[!htb]
 \centering
 \begin{tabular}{|c|c|c|c|c|}
\hline
 Name&Dept.&Phone&email&Comments \\ \hline
PDL & Hall-B&&&1nd contact \\ \hline
S. Stepanyan & Hall-B&&stepanya@jlab.org&contact \\ \hline
D. Kashy & Hall-B&&Kashy@jlab.org&contact \\ \hline
 \end{tabular}
\caption{ Personnel responsible for coordination of the HPS run and the torus assembly.} 
\label{tb:beam}
\end{table}

