\infolevone{
\chapter[Hall B Vacuum System]{Hall B Vacuum System
\label{chap:vacuum}
}
\footnote{Authors: S. Stepanyan \email{stepanya@jlab.org}}
}

\infoleveqnull{\section{Vacuum Systems}}
\indent

The Hall B vacuum system consists of three segments, all interconnected. The beam transport line consisting of $1.5$ to $2.5$ inch beam pipes, the Hall B tagger magnet vacuum chamber, and the set of vacuum chambers through the HPS detector system. Only the tagger vacuum chamber has a large window, $8$ inches over $30$ ft Kevlar-Mylar composite window. There is a $2.5$ in diameter $7$ mil Kapton window at the end of the HPS detector vacuum system, before the shielding wall, that is normally inaccessible. The vacuum in the system is provided by a set of rough, turbo, and ion pumps and it is maintained at the level of better than $10^{-5}$ Torr. 

\subsection{Hazards} 

\indent

Hazards associated with the vacuum system are due to rapid decompression in case of a window failure. Loud noise can cause hearing loss. Also, there is a hazard related to SVT coolant leaking into analyzing magnet vacuum chamber that will degrade the vacuum and may damage readout electronics if the leak is extensive.

\subsection{Mitigations}

\indent

All personnel working in the vicinity of the tagger vacuum chamber window are required to wear ear protection. Warning signs must be posted in that area. To mitigate a possible coolant leakage, the cooling system will be interlocked with the beamline vacuum system and the cooling system pressure gage. In an event of a leak, evident by increased vacuum system pressure or decreased cooling system pressure, the cooling system will be shutdown and valved off. 



\begin{safetyen}{10}{15}
\subsection{Responsible  personnel} 
\end{safetyen}
The vacuum system will be maintained by the Hall B engineering group. The authorized personnel is shown in table \ref{tab:vac:personnel}.
\begin{namestab}{tab:vac:personnel}{ Hall B vacuum system: responsible personnel}{%
       Hall B beamline: authorized personnel.}
  \TechonCall{\em 1st Contact}
  \DougTilles{\em 2nd Contact}
\end{namestab}


