%----------------------------------------------
%%% LSOP...
\section{Appendix: Laser Standard Operation Procedure}
\label{sec:lsop}

\subsection{ Introduction}

This LSOP describes the setup of the 
laser system, details the potential
hazards associated with the operation of this setup and provides instructions
for the safe and effective use of the equipment. In addition,
this manual provides information about the functioning of the various safety 
systems installed to protect personnel and equipment.

\subsection{Personnel}

The  lasers in Hall-B  may only be operated by
personnel who have :
\begin {itemize}
\item completed a Laser Safety course administrated by the laser safety officers at
Jefferson Laboratory (Patty Hunt).
\item read the Laser Safety section of the EH\&S Manual(6410);
\item  completed and passed an opthalmological exam;
\item had a safety walkthrough by the Laser Safety Supervisor;
\item read this document;
\item been added to the authorized list of Laser Personnel, included as the 
last page of this LSOP.
\end {itemize}
Jefferson Lab personnel or outside visitors, who have not completed all of 
above training, are
only allowed to enter the laser control area under the following conditions :
\begin {itemize}
\item be accompanied by a laser authorized personnel
\item if the laser is operational, with required safety
goggles
\item if any equipment, including the laser, is operational, no touching of
equipment due to electrical hazards.
\end {itemize}


\subsection{Laser}

The main Laser specifications are outlined in Table 1. For more specific
information, we refer to laser users manuals, 
which will be available in the lab.

\begin{table}
\begin{center}
\begin{tabular}{|l|l|}
\hline
& \\
{\bf Specifications}&{\bf XXXX} \\
\hline
& \\
\underline {\it Operational Specifications}& \\
Output power			& XX W \\
& \\
\underline {\it Mechanical Specifications}& \\
Weight			        & XX pounds  \\
Cooling Requirements 		& None required \\
.....\\
& \\
\underline {\it Operational Specifications}& \\
Typical Operating Temperature   & $0^\circ$C to $xx^\circ$C \\
Typical Storage Temperature     & $-20^\circ$C to $xx^\circ$C \\
Humidity (non-condensing)       & $5\%$ to $xx\%$  \\
& \\
\underline {\it Electrical Specifications}& \\
Input Power	                & xxx Vac 60 Hz, $<xxx$ W (xxx W typical) \\
& \\
\underline {\it Optical Specifications}& \\
Beam Characteristic 		& Semiconductor, multimode \\
....\\
\hline
\end{tabular}
\label{speclaser}
\caption{Laser specifications}
\end{center}
\end{table}


\subsection{Optical setup}

The optical setup...

\subsection{Hazards}

The primary beam hazards associated with lasers consists of eye 
injuries. The most severe eye injuries are caused by viewing the beam either directly
or through specular reflection. 

\subsection{Laser environment}

The lasers and the associated devices will be located in the .....
\subsection{Procedures}

In this section, we review the various procedures that are required to operate the
laser and optical devices. Hazards are least likely to occur during normal operation
when laser beams are switched on. During tests, maintenance,
upgrades and/or alignment,  beam hazards are more likely.

{\bf At all times}, when operating the diode lasers in lasing mode, safety goggles
are required.

\subsubsection{Normal procedure}
In the operation mode....

Thus the general procedures for normal operation of the lasers are:

\begin {itemize}
\item Enable laser safety interlock box;;
\item Wear protective eyewear;
\item Switch on AC power;
\item Turn on the control box with a key; 
\item Turn laser to Ready and then On.
\end {itemize}

\subsubsection{Alignment procedure}

All the mechanical stands supporting the optical components have been designed and
surveyed in order to achieve a preliminary safe alignment of the entire setup (laser
off).  Initial setup of laser and optical system will be done while the laser 
hut window is closed (such that no laser beam will come out the laser hut).

\subsubsection{Maintenance procedure}

Replacement of used or damaged optical components of the setup will be made with the
laser off (power switched off and unplugged).  The positions and orientations of the new components will be mechanically
surveyed and extensively checked before turning to any procedure needing the laser on.

In case of the failure of any electromechanical or electrical or electronic device,
the lasers and the other power supplies will be turned off and the out of order devices
will be fixed by Coherent service personnel. The Laser power
can simply be unplugged.


\subsubsection{Off-normal and emergency procedure}

In case of an emergency inform the laser safety officer (Patty Hunt, phone: 7039,
page: 584-7039). 


\subsection{Controls}

Several controls ....

All controls will be inspected every six months
and the inspection will be documented.

\subsection{Laser safety calculations}

\begin {enumerate}
\item {Maximum Permissible exposure}
\item {Optical Density}
\item {Nominal Hazard Zone}
The laser hazard zone is minimized by confining operation to an interlocked 
laboratory or interlocked enclosure.
\end{enumerate}


\subsection{List of authorized personnel}
The following personnel are authorized to operate the Coherent FAP-system
diode lasers and the associated polarized $^3$He target facility, under 
the assumptions, they
have completed the training requirements defined in Section 1:
\\ 
\begin{tabular}{ll}
Alexandre Deur          & Jefferson Lab \\
F.-X. Girod              & Jefferson Lab \\
\end{tabular}


\\ 

Names can be added to this list by the Laser System Supervisor.



%===========================================

\subsection{List of Laser Trained Personnel}
....

\begin{tabular}{ll}
Alexandre Deur          & Jefferson Lab \\
F.-X. Girod              & Jefferson Lab \\
\end{tabular}

\subsection{List of Authorized People to Change Target Cells}

\begin{tabular}{ll}
Alexandre Deur          & Jefferson Lab \\
F.-X. Girod              & Jefferson Lab \\
\end{tabular}


\subsection{List of Authorized People to Perform Laser Alignment}
\begin{tabular}{ll}

Alexandre Deur          & Jefferson Lab \\
F.-X. Girod              & Jefferson Lab \\
\end{tabular}

\vskip 0.3in
Names can be added to the above lists after proper training 
and authorized by...

\end{appendix}

