% Updated Comments Dec. 2
\infolevone{
\chapter[HPS Chicane Magnets]{HPS Chicane Magnets
\footnote{Authors: S. Stepanyan \email{stepanya@jlab.org}}
}
}

\infoleveqnull{
\section{HPS Chicane Magnets}
}
Dipole magnets can present magnetic and electrical hazards when they are energized. There is also hazard of an unwonted beam move due to the magnet power trip.  
The HPS experiment will use three magnet chicane installed on the beamline in the Hall B downstream alcove. The chicane includes the Hall B pair spectrometer magnet, an 18D36 dipole, with its vacuum chamber, and two identical H-dipoles known as "Frascati" magnets. Electron beam will pass through the magnets in the vacuum. The pair spectrometer magnet will serve as a spectrometer magnet. The two "Frascati" dipoles are to keep the deflected electron beam on the beamline to the dump. The spectrometer magnet will be powered from the Hall B pair spectrometer magnet power supply, Dthe "Frascati" magnets will be powered from so called "mini-torus" power supply, Dynapower ***.   

\subsection{Hazards} 
\indent

Dipole magnets can present magnetic and electrical hazards when they are energized. There is also hazard of an unwonted beam move due to the magnet power trip.  



\subsection{Mitigations}
\indent

There are plastic covers on the connection panels for power leads on the magnets for electrical safety. Any work around the magnets will require de-energizing the magnets, energized magnets are noted by read flashing beacons. Any work on the magnets requires the "Lock and Tag" procedures \cite{ehs}. There will be beacons installed to notify existence of the magnetic field. The magnet power supplies will be interlocked to the beam shutdown system (FSD). If any of power supplies will trip, beam delivery to Hall B will be interrupted.

\subsection{Responsible Personal}

The chicane magnets will be maintained by the Hall B engineering group.  

 \begin{table}[!ht]
 \centering
 \begin{tabular}{|c|c|c|c|c|}
\hline
 Name&Dept.&Phone&email&Comments \\ \hline
 Tech-on-call & Hall-B&&& 1st contact  \\ \hline
 D. Tilles & Hall-B&&tilles@jlab.org&2nd contact \\ \hline
  \end{tabular}
\caption{ Personal responsible for the HPS chicane.} 
\label{tb:beam}
\end{table}
